%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\centering\textbf{\href{https://www.linkedin.com/in/rahul-damineni/}{\Large Rahul Damineni}} \\
\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  E-mail: \href{mailto:daminens@oregonstate.edu}{daminens@oregonstate.edu}  & Mobile: +1-541-905-1304\\ 
  \href{https://www.github.com/RahulDamineni/}{github.com/RahulDamineni/} & \href{https://www.linkedin.com/in/rahul-damineni/}{linkedin.com/in/rahul-damineni/}
\end{tabular*}

\vspace{-5pt}
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Oregon State University}{Corvallis, OR}
      {Master of Science in Computer Science;  \textcolor{MidnightBlue}{\href{https://github.com/RahulDamineni/osu-courses-and-misc}{(coursework)}};       GPA: \textcolor{Black}{3.67}}{September 2019 -- \textcolor{Black}{June 2021}}
      \vspace{-5pt}
    \resumeSubheading
      {BITS, Pilani}{Hyderabad, IN}
      {Master of Science in Physics, Bachelor of Engineering in Electrical \& Electronics}{August 2011 -- July 2016}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {CloudSek Infosec}{Bangalore, IN}
      {Sr. Machine Learning Engineer}{August 2016 - September 2018}
      \resumeItemListStart
        \resumeItem{Achievement}
          {Conceived and developed several high-value features in the core product.}
        \resumeItem{ML APIs as a service}
          {Developed an async RESTful micro-service that served 200k requests per day. The design accommodates worker scaling, A/B testing \& adding new models. It uses a publish-subscribe pattern to be fault-tolerant and scale workers on demand. \texttt{Python-Flask, RabbitMQ, MongoDB, NginX} \textcolor{MidnightBlue}{}}
        \resumeItem{Threat Detector}
          {Collected \& classified thousands of tweets, forum \& blog posts to identify mentions related to vulnerabilities, data breaches, and cyber threats. Engineered a Hierarchical Attention-based RNN which improved the task accuracy by 13\%. \texttt{Python-Requests, Selenium, Keras, TensorFlow} \textcolor{MidnightBlue}{}}
        \resumeItem{Fake Domain Finder}
          {Discovered 100+ malicious websites impersonating trademarks of clients by building a cloud monitor. Made pipelines for data collection, training, and inference around text classification \& template matching skills. \texttt{Sklearn, OpenCV, MongoDB, Selenium, SystemUtils} \textcolor{MidnightBlue}{}}
      \resumeItemListEnd

    \resumeSubheading
      {UNAR Labs}{Portland, ME}
      {AI/ML Research Intern}{June 2020 - October 2020}
      \resumeItemListStart
        \resumeItem{SAT Digitalizer Service}
          {Developed \& deployed a general-purpose job scheduler that batch-processes digitization jobs and exposes the results through a REST API. The stack was containerized \& orchestrated using docker-swarm. \texttt{Redis Queue, SQLAlchemy, PostgreSQL, Docker, Python-Flask} \textcolor{MidnightBlue}{}}
        % \resumeItem{Plot2Data}
        %   {To communicate graphical data to visually impaired users, training a neural network to generate tabular data from images. Data is automatically generated using plotting libraries, augmented by extracting text using OCR, annotating textual regions, and generating features using RNN \& CNN based encoders. \textcolor{MidnightBlue}{}}
      \resumeItemListEnd

    \resumeSubheading
      {TheMathCompany}{Bangalore, IN}
      {Associate (Data Science)}{September 2018 - April 2019}
      \resumeItemListStart
        \resumeItem{Achievement}
          {Optimized a supply chain component that would bridge the gap in production goals and save \$15M annually by collaborating with stakeholders and the engineering team at Kimberly Clark}
        \resumeItem{Plan Rate Forecasting}
          {Predicted throughput of production mills by performing exploratory data analysis (EDA) to identify influential parameters, conceived and tested hypotheses, engineered features, and trained a predictive model that forecasts rate with 7\% MSE. Packaged this model as a simulator for the end consumer. \textcolor{MidnightBlue}{}}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Clip-tionary}
      {To memorize and pronounce a new word easily, shows scenes from TV shows and movies where it was uttered. \texttt{ReactJS, Python-Flask, MongoDB, Docker, WebRTC} \textcolor{MidnightBlue}{\href{https://github.com/RahulDamineni/tv-dict}{(code)} \href{https://github.com/RahulDamineni/tv-dict/blob/master/CS562_ProjectSketch.pdf}{(design document)}}}
    \resumeSubItem{Anonymous Author Identifier}
      {To identify latent clues in writing styles, trained an LSTM based binary classifier, and a DBMS program that determines if a text is written by existing authors in DB. \texttt{PyTorch, torchtext} \textcolor{MidnightBlue}{\href{https://github.com/RahulDamineni/anonymous_author_matcher}{(code)} \href{https://github.com/RahulDamineni/anonymous_author_matcher/blob/master/anon_author_identifier_report.pdf}{(report)}}}
    \resumeSubItem{DARPA Subterranean Challenge}
      {Trained a MobileNet with Single Shot Detector head to detect and localize the competition's artifacts with mAP of 58\% (@0.75 IoU). \texttt{nvidia-docker, TensorFlow Object Detection API} \textcolor{MidnightBlue}{\href{https://www.subt-explorer.com/}{(website)}}}
    \resumeSubItem{Super Logger}
      {Project planning and logistics management platform for road construction projects. Surveyed for user stories, designed a data harvesting framework around the actors, and developed most of the MVP. \texttt{ReactJS, NodeJS, MongoDB, Docker, GCP: compute engine, container registry, GKE} \textcolor{MidnightBlue}{\href{https://drive.google.com/file/d/1H9IJ4kVDP79thjI6kPTr0LBxHkd46nlo/view?usp=sharing}{(pitch)}}}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\vspace{-5pt}
\section{Skills \& Tools}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python, JavaScript, C, Shell Scripting, SQL}
    }
    \item{
      \textbf{Frameworks}{: PyTorch, Scikit-Learn, OpenCV, Pandas, SQLAlchemy, Matplotlib, TensorFlow, ReactJS, Flask, Selenium}
    }
    \item{
      \textbf{Tools}{: Git, MongoDB, PostgreSQL, Docker, AWS: EC2, DynamoDB, S3; GCP: Cloud Run, Storage, Container Registry}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------

%---------KEYWORDS FOR ATS------------------
\vspace{-3pt}
\tiny\textcolor{White}{Keywords: Industry Experience, Algorithm, Software Development, Full stack application, Machine Learning, Natural Language Processing, Computer Vision}
\vspace{-10pt}
\tiny\textcolor{White}{Deep Learning, Data Visualization, Predictive Analysis, Clustering \& Classification, Web Scraping, Model Development, Model Evaluation, Scalable Pipelines, SQL}
\vspace{-10pt}
\tiny\textcolor{White}{Numpy, Sklearn, Linear Regression, XGBoost, word2vec, ELMo word embedding, BERT, Decision Trees, CART, Random Forests, Ensemble Models}
\vspace{-10pt}
\tiny\textcolor{White}{Machine Learning Engineer, Software Engineer, Software Developer, DevOps, Data Engineer, SDE I, SDE II, Agile Development, Websockets}
%---------KEYWORDS FOR ATS------------------
\end{document}
